Understanding the impact of electronically-delivered parenting advice

### 2019-02-11 paper/cogsci2019/cogsci2019.Rmd
formatting

### Participants. 
`r nrow(d)` infants  (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n= 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). Sixty-one% of participants (n=37) had been exposed to 2 or more languages as indicated by their parent. Parents identified their children as White (n=25), Asian (n=11), African American/Black (n=2), Biracial (n=12), other (n=5), or declined to state (n=5). Fifteen parents reported their child was of Hispanic origin. Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n=6).

@@

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p<0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p<0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p<0.05) for length of passive joint attention.

>>>>

### Participants. 
`r nrow(d)` infants  (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). Sixty-one% of participants (n = 37) had been exposed to 2 or more languages as indicated by their parent. Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). Fifteen parents reported their child was of Hispanic origin. Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n = 6).

@@

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p < 0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p < 0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p < 0.05) for length of passive joint attention.

### 2019-02-11 paper/cogsci2019/cogsci2019.tex
formatting

60 infants (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20
12-17.9 month-olds, and 20 18-24 month-olds) and their parents
participated in a museum in northern California. We included infants who
were exposed to English at least 50 percent of the time (n= 58) or who
were exposed less but whose participating parent reported that they
primarily speak English with their child at home (n = 2). Sixty-one\% of
participants (n=37) had been exposed to 2 or more languages as indicated
by their parent. Parents identified their children as White (n=25),
Asian (n=11), African American/Black (n=2), Biracial (n=12), other
(n=5), or declined to state (n=5). Fifteen parents reported their child
was of Hispanic origin. Parents tended to be highly educated, with a
highest level of education reported as high school (n = 5), some college
(n = 6), four-year college (n = 14), some graduate school (n = 1),
completed graduate school (n = 28) or declined to state (n=6).

@@

The video of each session was manually coded for episodes of joint
attention using the Datavyu software. The video taken at floor level was
coded by default, but the other video was referred to if the
participants were not visible or if there was a technological error with
the first camera. For each participant we coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. We defined parental bids for joint
attention as any attempt to initiate joint attention (i.e label, point,
or otherwise draw attention to an object) that does not result in
passive or coordinated joint attention. If more than 3 seconds elapsed
between bids, they were coded as separate attempts. An episode of joint
attention was considered passive if both participants visually focused
on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. Episodes
joint attention were considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent. This could be looks to the
parent's face, gestures, vocalizations, or turn-taking. If either
participant looked away for less than 3 seconds and then returned to the
same object, it was coded as part of the same period of joint attention.
A second coder independently coded a third of the videos (i.e., 20 of
the 60 videos, approximately equally distributed across ages) to
establish reliability. The two coders achieved reliability with ICC =
0.80 with 95\% confident interval = 0.57-0.92 (p\textless{}0.05) for
number of parent bids; ICC = 0.20 with 95\% confident interval =
-0.26-0.58 for number of passive joint attention established; ICC = 0.66
with 95\% confident interval = 0.32-0.85 (p\textless{}0.05) for number
of coordinated joint attention established; ICC = 0.24 with 95\%
confident interval = -0.21-0.61 for length of passive joint attention,
and ICC = 0.62 with 95\% confident interval = 0.27-0.83
(p\textless{}0.05) for length of passive joint attention.

>>>>

60 infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20
12-17.9 month-olds, and 20 18-24 month-olds) and their parents
participated in a museum in northern California. We included infants who
were exposed to English at least 50 percent of the time (n = 58) or who
were exposed less but whose participating parent reported that they
primarily speak English with their child at home (n = 2). Sixty-one\% of
participants (n = 37) had been exposed to 2 or more languages as
indicated by their parent. Parents identified their children as White (n
= 25), Asian (n = 11), African American/Black (n = 2), Biracial (n =
12), other (n = 5), or declined to state (n = 5). Fifteen parents
reported their child was of Hispanic origin. Parents tended to be highly
educated, with a highest level of education reported as high school (n =
5), some college (n = 6), four-year college (n = 14), some graduate
school (n = 1), completed graduate school (n = 28) or declined to state
(n = 6).

@@

The video of each session was manually coded for episodes of joint
attention using the Datavyu software. The video taken at floor level was
coded by default, but the other video was referred to if the
participants were not visible or if there was a technological error with
the first camera. For each participant we coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. We defined parental bids for joint
attention as any attempt to initiate joint attention (i.e label, point,
or otherwise draw attention to an object) that does not result in
passive or coordinated joint attention. If more than 3 seconds elapsed
between bids, they were coded as separate attempts. An episode of joint
attention was considered passive if both participants visually focused
on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. Episodes
joint attention were considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent. This could be looks to the
parent's face, gestures, vocalizations, or turn-taking. If either
participant looked away for less than 3 seconds and then returned to the
same object, it was coded as part of the same period of joint attention.
A second coder independently coded a third of the videos (i.e., 20 of
the 60 videos, approximately equally distributed across ages) to
establish reliability. The two coders achieved reliability with ICC =
0.80 with 95\% confident interval = 0.57-0.92 (p \textless{} 0.05) for
number of parent bids; ICC = 0.20 with 95\% confident interval =
-0.26-0.58 for number of passive joint attention established; ICC = 0.66
with 95\% confident interval = 0.32-0.85 (p \textless{} 0.05) for number
of coordinated joint attention established; ICC = 0.24 with 95\%
confident interval = -0.21-0.61 for length of passive joint attention,
and ICC = 0.62 with 95\% confident interval = 0.27-0.83 (p \textless{}
0.05) for length of passive joint attention.
